### 2023-06-22 tex/lr.tex
[ add ] note on subusaging order

>>>>

Note that my subusaging order is reversed relative to the similar ordering found
in previous work --- particularly \citet{Granule18} and related work from those
authors.
I find the order I use preferable because it matches the standard for
simultaneous renaming and substitution (we will see later that a
$\leq$-relationship between contexts gives rise to a renaming), and all of these
make rules like \TirName{Subuse} interpretable as generalised notions of
composition between orderings/renamings/substitutions and terms.
